### 2014-09-11 D1-3.tex
Added Privacy Protection tex from Max.
Signed-off-by: Heinrich Hartmann <hartmann@uni-koblenz.de>

@@

\chapter{Privacy Protection}
Intro
\section{Historical Definitions}
Aristotle
Warren and Brandeis
Fried
\section{Privacy Definition and Taxonomy}
\section{Privacy and Law}
European Convention on Human Rights - Article 8
EU Data Protection Direvtive
\section{IT Security Analysis}
Live+Gov Privacy Protection Analysis
Step 1. World Analysis
Assets: Privacy
IT-Systems and Humans
Conflict of Interests
Vulnerabilities
Step 2. Potential Analysis
Step 3. Plan Development
\section{Implementation}
* Sensor Data Privacy Control
* Rising Awareness

>>>>

\input{PrivacyProtection-2014-09-09}

@@

\section{Implementation}
\subsection{Authentification and Access Control}
\subsection{Anonymization and Pseudonoymization}
\subsection{Randomization}
